Supplementary material

### 2017-10-17 Manuscript/ms.tex
Adding a few citations

Dengue fever is a massive global public health burden, with millions of cases per year in Brazil alone \cite{Bhatt2013}.  
Since the dengue virus (DENV) is vectored by the mosquito \textit{Aedes aegypti}, dengue fever is prevented primarily through mosquito control programs \cite{Achee2015}.
To be effective, control efforts should be guided by consistent, high resolution mosquito surveillance \cite{Morrison2008}.
The "MI-Dengue" system, implemented by the company Ecovec and deployed throughout cities in Brazil, uses a city-wide grid of mosquito sticky-traps (MosquiTRAPs) for spatial prioritization of source reduction and larvicide application \cite{Eiras2009}.
Comparing cities with and without this system, \cite{Pepin2013} estimated that it prevented 27,191 cases of dengue fever from 2007 - 2011.
Though this system has been effective, the mosquito indices and thresholds used to prioritize control efforts remain somewhat ad-hoc.
As noted in \cite{Morrison2008}, entomological indices are only relevant in the context of local epidemiology, and thus control policies will be most effective when they synthesize both entomological and clinical surveillance.

Many of the attempts to link these two sources of information have found a weak relationship between mosquito surveillance and disease risk (CITATIONS).
These efforts have often relied on tests of the ability of mosquito abundance measures to predict human disease risk in regression models.
For example, \cite{Pepin2015} found that models that included MosquiTRAP surveillance data failed to predict weekly dengue cases any better than models that included lagged case data alone.
However, such tests fail to account for the mechanistic, non-linear relationship between mosquito population dynamics and dengue epidemiology.
The cycle of transmission between humans and dengue is controlled not just by mosquito abundance, but also by mosquito survival relative to the virus' incubation period \cite{Achee2015}.
In fact, whether or not an exposed mosquito will survive long enough to become infectious represents a critical bottleneck in the transmission process.

>>>>

Dengue fever is a massive global public health burden, with millions of cases per year in Brazil alone \cite{Bhatt2013}.  
Since the dengue virus (DENV) is vectored by the mosquito \textit{Aedes aegypti}, dengue fever is prevented primarily through mosquito control programs \cite{Achee2015}.
To be effective, control efforts need to be guided by consistent, high resolution mosquito surveillance \cite{Morrison2008}.
The "MI-Dengue" system, implemented by the company Ecovec and deployed throughout cities in Brazil, uses a city-wide grid of mosquito sticky-traps (MosquiTRAPs) for spatial prioritization of source reduction and larvicide application \cite{Eiras2009}.
Comparing cities with and without this system, \cite{Pepin2013} estimated that it prevented 27,191 cases of dengue fever from 2007 - 2011.
Though this system has been effective, the mosquito indices and thresholds used to prioritize control efforts remain somewhat ad-hoc.
As noted in \cite{Morrison2008}, entomological indices are only relevant in the context of local epidemiology, and thus control policies will be most effective when they synthesize both entomological and clinical surveillance.

Many of the attempts to link these two sources of information have found a weak relationship between mosquito surveillance and disease risk \cite{Bowman2014, Cromwell2017}.
These efforts have often relied on tests of the ability of mosquito abundance measures to predict human disease risk in regression models.
For example, \cite{Pepin2015} found that models that included MosquiTRAP surveillance data failed to predict weekly dengue cases any better than models that included lagged case data alone.
However, such tests fail to account for the mechanistic, non-linear relationship between mosquito population dynamics and dengue epidemiology.
The cycle of transmission between humans and dengue is controlled not just by mosquito abundance, but also by mosquito survival relative to the virus' incubation period \cite{Achee2015}.
In fact, whether or not an exposed mosquito will survive long enough to become infectious represents a critical bottleneck in the transmission process.
